Gray-Box Optimization using the Parameter-less Population Pyramid

### 2015-02-04 Gray Box Optimization using the Parameter-less Population Pyramid/main.tex
Updated abstract

\maketitle
\begin{abstract}
%Maximum 200 Words

Unlike black-box optimization problems, gray-box optimization problems have known,
limited-cardinality non-linear relationships between variables. This domain contains many
real world problems with examples in network security, computational biology, VLSI design, and statistical physics.
Leveraging these restrictions, the Hamming-Ball Hill Climber
(HBHC) can efficiently find r-bit local optima. We show how a
simple memetic algorithm in conjunction with HBHC can find \emph{global}
optima for some gray-box problems. We also develop a gray-box version of the Parameter-less
Population Pyramid (P3), utilizing both the HBHC and the known information about variable relationships,
which outperforms all of the examined algorithms.

>>>>

\maketitle
\begin{abstract}
%Maximum 200 Words
Unlike black-box optimization problems, gray-box optimization problems have known,
limited, non-linear relationships between variables. Though more restrictive, gray-box problems include many
real-world applications in network security, computational biology, VLSI design, and statistical physics.
Leveraging these restrictions, the Hamming-Ball Hill Climber
(HBHC) can efficiently find r-bit local optima. We show how
1) a simple memetic algorithm in conjunction with HBHC can find \emph{global}
optima for some gray-box problems and 2) a gray-box version of the Parameter-less
Population Pyramid (P3), utilizing both the HBHC and the known
information about variable relationships, outperforms all of the
examined algorithms.
